Verifying Demonstrations

### 2017-10-03 protocol.tex
Edits and moves temporal eligibility of protocol, adds overview

With the above properties, \cref{CreatedBeforeEnd} is straight-forward: Alice 
and Bob simply commit their proofs to the blockchain as soon as possible after 
they have participated in the protest.
Thus we can infer that a proof (or proof share) was created at the latest when 
it was committed.
For \cref{CreatedAfterStart}, Alice and Bob must include the hash value of an 
existing block in the blockchain.
Then it is clear that the proof must have been created after that block (since 
predicting such a value is hard).

\subsubsection{Linkability and designated protest}

\Cref{CountOnce} is required to prevent Sybil attacks, i.e.\ that one 
individual can provide two proofs of participation and thus be counted twice.
That situation should be detectable.
We can do this by ensuring that Alice cannot produce two valid proofs which
are unlinkable.
This can be done by including a signature made by a verified key.
(We will discuss the privacy aspects in \cref{Privacy}.)

\Cref{DesignatedEvent} focuses on the problem that there might be a counter 
protest at the same time and place, these would have the same spatial and 
temporal properties.
To distinguish them, we also need to prove for which of these events that a 
proof is designated.
This can be achieved by a unique identifier for a protest, e.g.\ the hash of 
its \enquote{manifesto}.

\begin{frame}
\begin{figure}
  \centering
  \mode<presentation>{%
    \only<1>{%
      \begin{tikzpicture}
        \tikzset{grow'=right,level distance=5em}
        \Tree [.proof
        {share}
        [.{share} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ]
        %[.tsig {$t_s''$} ]
        ]
        {share}
        ]
      \end{tikzpicture}
    }
  }
  \only<2>{%
    \begin{tikzpicture}
      \tikzset{grow'=right,level distance=5em}
      \Tree [.proof
      {share}
      [.{share} {\(x,y\)} {$t_s$} [.{osig} 
      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ]
      %[.tsig {$t_s''$} ]
      ]
      {share}
      ]
    \end{tikzpicture}
  }
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (share), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the \ac{tposet}.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnessed by a trusted witness (tsig).
    }
  }
\end{figure}

@@

>>>>

An overview of the structure of a proof is available in \cref{ProofFig}.

\begin{frame}
\begin{figure}
  \centering
  \mode<presentation>{%
    \only<1>{%
      \begin{tikzpicture}
        \tikzset{grow'=left,level distance=5em}
        \Tree [.proof
        {share}
        [.{share} {\(x,y\)} {$t_s'$} [.{\color{red}osig} {$t_s$} ]
        %[.tsig {$t_s''$} ]
        ]
        {share}
        ]
      \end{tikzpicture}
    }
  }
  \only<2>{%
    \begin{tikzpicture}
      \tikzset{grow'=left,level distance=5em}
      \Tree [.proof
      {share}
      [.{share} {\(x,y\)} {$t_s'$} [.{osig} 
      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s$} ]
      %[.tsig {$t_s''$} ]
      ]
      {share}
      ]
    \end{tikzpicture}
  }
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (share), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the \ac{tposet}.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnessed by a trusted witness (tsig).
    }%
    \label{ProofFig}
  }
\end{figure}

@@

\subsubsection{Temporal eligibility}

Given the properties of the storage (in \cref{StorageProperties}), 
\cref{CreatedBeforeEnd} is straight-forward: Alice and Bob simply commit their 
proofs to the blockchain as soon as possible after they have participated in the 
protest.
Thus we can infer that a proof (or proof share) was created at the latest when 
it was committed.
For \cref{CreatedAfterStart}, Alice and Bob must include the hash value of an 
existing block in the blockchain (\(t_s\) in \cref{ProofFig}).
Then it is clear that the proof must have been created after that block (since 
predicting such a value is hard).
